---
title: "VariableSearch"
output: html_document
date: '2022-07-09'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
library(car)
library(dplyr)
library(tidyquant)
library(quantmod)
library(lubridate)
library(xts)
library(ggplot2)
library(forecast)
```

# Time Series Assumptions:

1.  Stationary: Properties of the time series don't depend on the time when it was captured. **Specifically, the mean, variance and autocorrelation structure do not change over time.**
    1.  If a series is not stationary, we can transform it to be stationary. Using one of the following:

        1.  Used differenced data

        2.  Fit a curve to the data then model the residuals from the fit.

        3.  Log or Square root transform when non constant variance.
2.  Univariate **ARIMA works on a single variable. Auto-regression is all about regression with the past values.**

# Load in SPY data 

```{r}

tickers = c("SPY", "TLT") # Market and a risk free asset 

prices <- tickers %>% 
  tq_get(get = "stock.price", from = as.Date('2018-01-01'), to = as.Date('2022-07-09')) %>% 
  select(date,ticker = symbol, close) %>%
  mutate(date = as.Date(date)) 

price_monthly_ret = prices %>% group_by(ticker) %>%
  tq_transmute( select = close, mutate_fun= periodReturn, period = 'daily', colname = 'monthly_return')

```

# Closing Price

```{r pressure, echo=FALSE}
 prices %>%
  filter(ticker=='SPY') %>%
  ggplot(aes(x = date, y = close)) +
    geom_line() +
    labs(title = "SPY Line Chart", y = "Closing Price", x = "") + 
    theme_tq()
```

# Returns 
```{r}
spy_ret = price_monthly_ret %>% filter(ticker == 'SPY')
spy_ret %>%
  ggplot(aes(x = date , y = daily.returns)) + geom_line()

mean(spy_ret$monthly.returns) # Mean approx 0
sd(spy_ret$monthly.returns)^2 # Variance approx 0 

spy_timeSeries = xts(spy_ret[,-c(1,2)], order.by= as.Date(spy_ret$date))

par(mfcol = c(2,1))
acf(spy_timeSeries, lag.max = 10, main = '')
pacf(spy_timeSeries, lag.max = 10, main = '')
```

```{r}
fitARIMA <- arima(spy_timeSeries, order=c(0,0,0),seasonal = c(1,1,1),method="ML")
futurVal <- forecast(fitARIMA,h=3, level=.95)
summary(fitARIMA)
plot(futurVal)

```

```{r}
lag(spy_ret, 1)
Cumula
```































